\chapter{Complex Networks}
\label{chap:complexnetworks}

Complex networks can describe many systems which are observed in nature and society \cite{newmannetworks}, such as computer networks, food chains, protein structures, etc. 
They are generally divided into four categories:

\begin{enumerate}
	\item \textbf{Technological Networks} are grids purposefully engineered to provide services to consumers and/or citizens.
	 	The primary examples of these networks are the Internet, the telephone network, power grids, transportation and delivery networks.
	 	A commonly studied type of technological network are Mobile Ad-hoc Networks (MANETs), networks of mobile devices which communicate with each other without the need of a centralized agent.
		Although not of widespread use, MANETs can provide a way to create a network without pre-existing infrastructure, as long as each device is equipped with the proper hardware and software.
		Trust issues in technological networks and MANETs are detailed in \autoref{section:trusttechnological}.
		VANETs, which are special types of MANETs, will be introduced in \autoref{chap:vanets}, along with several details regarding trust in those types of networks.
	\item \textbf{Social Networks} are formed of relationships between people, or groups of people.
		These relationships can be familiar, friendships, acquaintance, etc.
		For the purposes of this work, the most relevant type of relationship is that of trust.
		The details surrounding trust relationships in social networks are shown in \autoref{section:trustsocial}.
	\item \textbf{Information Networks} are the ones in which nodes are pieces of data or information and the edges are the connections between those pieces.
		Often, information networks are directly associated with technological or social networks.
		For instance, while the World Wide Web is an information network (in which the nodes are webpages and the edges are the links that users click on to navigate), it relies on the Internet, as is contains the physical infrastructure that makes the web possible.
		Online social networks can also be classified as information networks, since their nodes are actually information about people rather than the people themselves.
	\item \textbf{Biological Networks} are the networks found in nature.
		Their nodes can be chemicals, cells, animals, groups of lifeforms, and more.
		The brain contains a neural network formed by neurons, cells which enable information processing; connections in the network represent signals that are sent from one neuron to another.
		Another instance of biological networks are food chains, categorized as ecological webs.
		Species of animals are the nodes, while the predation of other species form the edges.
		
\end{enumerate}

While issues of trust have been studied on most types of networks, this work will emphasize on social and technological networks, for two reasons: first, these are the most studied types of networks in the field of computer science; and second, previous study on both can provide useful insights towards trust in vehicular networks.
It is clear that VANETs are part of technological networks; in this work, however, it is also argued that they have social network features, which is why they will also be described in this chapter. 

%As this work relates to trust issues in complex networks, it is interesting to further examine social networks and the importance of trust within them.
%While the end result of the study will be applied to technological networks, certain aspects of social networks provide useful analogies to trust management in other kinds of networks.

\section{Trust in Social Networks}
\label{section:trustsocial}
In a traditional social network, it is simple to perceive how trust is relevant and how it works, since trust relationships between people (friends, relatives, colleagues, etc.) are used on a daily basis to make decisions.
When adapted to a digital environment, these social relationships can be used to automatically increase the relevance of certain information.
For instance, upon reading an online review for a certain product, a user will be more likely to accept the review's conclusion if it was written by a close friend than if it were written by a stranger.
Furthermore, if the review was written by a person who the user knows to be malicious or uninformed, its contents will be even less relevant.
In short, trust is a way of estimating how much a certain recommendation will lead to a positive outcome. \cite{golbeck2006inferring}

Social networks also have the property of carrying trust from one relationship to another:
information shared by a close friend of a person might be considered almost as trustworthy as some collected by the person him or herself.
Therefore, it is possible to model social trust relationships as a graph, in which nodes represent people and edges represent a certain degree of trust.
Friends of friends \cite{boissevain1974friends} might not have very high trust values, but could still be considered more trustworthy than the average stranger.
This property is similar, but not identical, to transitivity, since trust is diminished for each extra step an origin node needs to reach a destination, and there is also the possibility that one node distrusts another even if they share a mutual friend.

In general, social networks are mostly static.
Although friendships are formed and ended frequently, those connections do not disrupt the general shape of the network, because members of the network will usually have other friends to rely on.
Even if a certain person's trust integrity is compromised due to a specific incident, that person's friends are not necessarily also deemed untrustworthy, preserving part of the trust graph.

%Many works exist regarding trust relationships in complex networks, and in social networks in particular.
%Here, only a few examples will be described, in order to show the general idea of trust research for these types of networks.

\section{Trust in Technological Networks}
\label{section:trusttechnological}
In conventional technological networks, such as the Internet, trust is defined and applied quite differently from social networks.
Generally, trust is very centralized through services that offer security to users.
Examples of this can be a IP filtering to avoid distributed denial of service (DDoS) attacks or web browser extensions that block requests to domains in a blacklist.
However, all these centralized solutions would be too slow to be viable in a dynamic and ad-hoc network.

MANETs require a decentralized approach to trust management and, therefore, are more similar to social networks.
In both cases, each member of a network has its own opinions about other members, and these opinions can change over time.
However, while social networks are mostly static, the topology of a MANET changes frequently as nodes move around.
[Perhaps this is a good place to mention trust vs. trust management]
Nodes must be able to handle trust with its immediate neighbors for any given moment, so it can properly filter out potentially malicious data.
In networks in which nodes can meet more than once, it may be valuable to store information from previous encounters to use in the future, although this process can be too slow or resource-consuming to be viable in certain devices.

The most common instance of MANETs is using mobile devices, such as smartphones, being carried by humans.
Although these networks are dynamic, their mobility is relatively low in relation to the wireless range of the devices — if two people are walking in opposite directions, their phones may communicate for several seconds before they leave each other's range.
Trust solutions for MANETs use this property to their advantage, since it allows one node to test another and check several of the messages sent between them.

Another important aspect of trust in ad-hoc networks is that information is, generally, uncertain and incomplete \cite{baras2005cooperation}.
That is, since nodes form their own model and opinions of the surrounding network, it is unlikely that this data will be certain and accurate with reality.
For this reason, it is also possible to use data gathered by neighboring nodes to complement the model.
This data itself is subject to the trust evaluation of the neighbors, but it is crucial to better approximate the trust values of other nodes.
Incompleteness is an inherit trace of MANETs, since it is entirely possible for nodes to be too distant to communicate, and only occasionally come into contact.

Finally, MANETs of mobile devices must take into consideration the processing and battery limitations of those devices.
Nodes may disable wireless communications to save power and therefore become uncooperative, or it may be too slow to be a reliable source of information.

%=====================================================
